\documentclass[oneside, english, 10pt, a4paper]{memoir}
\usepackage{CV_template}

\SetFirstName{Pierre}
\SetLastName{Kibleur}
\SetTitle{PhD, Engineer}
\SetAddress{Coupure Links 393, 9000 Ghent, Belgium}
\SetPhone{+33 (0)6 09 90 18 77}
\SetEmail{pierre.kibleur@gmail.com}
\SetNationality{French}
\SetExtra{Feb 17\textsuperscript{th}, 1993}
\SetDate{2022}

\begin{document}
    \header
    \section{Experience}
   		\CVentry[UGCT, Ghent, Belgium]
			{Research scientist: X-ray computed tomography applied to wood fiber materials. }
			{2018-2022}{Dynamic experiments, chemical doping, dual-energy, deep learning, digital image correlation, finite element modeling. Author in 11 peer-reviewed publications, presenter at 6 international conferences}{}    
    
        \CVentry[Confinis AG, Geneva, Switzerland]
			{Consulting in regulatory compliance for medical devices}{2018}{}{}

        \CVentry[University of Fribourg, Fribourg, Switzerland]
            {Research scientist: biorobotics. Preparation of a peer-reviewed publication}{2018}{}{}

        \CVentry[GTX medical, Lausanne, Switzerland]
            {Robotics intern. Programming, integration of sensors, automation of the code's unit testing }
            {2017}{}{}

    \section{Education}
   		\CVentry[Ghent University, Ghent, Belgium]
		{PhD in bioscience engineering}
		{2018-2022}{}{}    

		\CVentry[EPFL, Lausanne, Switzerland]
		{MSc in computational science and engineering}{2015--2018}
		{BSc in physics}{2011--2015}
		
		\CVentry[ULB, Brussels, Belgium]
		{Erasmus+ exchange, physics}{2014--2015}{}{}
		
		\CVentry[Lyc\'ee Saint-Michel de Picpus, Paris, France]
		{High school diploma in sciences}{2011}{}{}
        
    \section{Technical skills}
        \OneLiner[Programming]{C/C++, Python, Matlab, Bash, CUDA, Basic}{}
        \OneLiner[Libraries]{Pandas, Scipy, skimage, OpenCV, tikz, TwinCAT, OpenSim, TensorFlow}{}
        \OneLiner[Software]{Dragonfly, Avizo, Fiji, Abaqus, Solid Works}{}
        \OneLiner[Environments]{Linux/Windows, Vim, Atom, Visual Studio, Jupyter, Overleaf}{}
        \OneLiner[Office]{LaTeX, Pack Office, Visio}{}
        \OneLiner[Version control]{Git, Team Foundation Server}

    \section{Teaching}
        \OneLiner[Supervision]{Three master theses on precision imaging; deep learning; robotics}{2020-2022}
        \OneLiner[Tutoring]{Analysis III for physicists ($\sim$20 students)}{2016}
        
    \section{Languages}
		\OneLiner[French/English]{Fluent \hfill}{}
		\OneLiner[Russian/Dutch]{Limited proficiency\hfill}{}
		
	\section{Free time}
		\OneLiner[Sports]{Rowing (Belgian champion M8+, 2021), running, swimming}{}
		\OneLiner[Music]{Flute and tenor saxophone}{}
		        
     \section{Peer-reviewed publications}

\begin{itemize}    	    	
	\item \textbf{Pierre Kibleur}, Benjamin Blykers, Matthieu N. Boone, Luc Van Hoorebeke, Joris Van Acker, and Jan Van den Bulcke. Detecting thin adhesive coatings in wood fiber materials with laboratory-based Dual-Energy Computed Tomography (DECT), \emph{Scientific Reports}, 2022.
	
	\item  {\textbf{Pierre Kibleur}, Zaira Manigrasso, Wannes Goethals, Jan Aelterman, Matthieu N. Boone, Joris Van Acker, and Jan Van den Bulcke}. {Microscopic deformations in MDF swelling: a unique 4D-CT characterization}, \emph{Materials and Structures}, 2022.
		
	\item  {\textbf{Pierre Kibleur}, Jan Aelterman, Matthieu N. Boone, Jan Van den Bulcke, and Joris Van Acker}. {Deep learning segmentation of wood fiber bundles in fiberboards}, \emph{Composites Science and Technology},  2022.
	
	\item Haichao Li, Jan Van den Bulcke, \textbf{Pierre Kibleur}, Orly Mendoza, Stefaan De Neve, and Steven Sleutel. Soil textural control on moisture distribution at the microscale and effect on organic matter mineralization, \emph{Soil Biology and Chemistry}, 2022.
	
	\item {Wanzhao Li, Zheng Zhang, Changtong Mei, \textbf{Pierre Kibleur}, Joris Van Acker, and Jan Van den Bulcke}. {Understanding the mechanical strength and dynamic structural changes of wood-based products using X-ray computed tomography}, \emph{Wood Material Science {\&} Engineering}, 2022.
	
	\item {Yuriy Sinchuk, \textbf{Pierre Kibleur}, Jan Aelterman, Matthieu N. Boone, and Wim Van Paepegem}. {Geometrical and deep learning approaches for instance segmentation of CFRP fiber bundles in textile composites}, \emph{Composite Structures}, 2021.
	
	\item {Jure \v{Z}}igon, Matja{\v{z}} Pavli{\v{c}}, \textbf{Pierre Kibleur}, Jan Van den Bulcke, Marko Petri{\v{c}}, Joris Van Acker, and Sebastian Dahle. {Treatment of wood with atmospheric plasma discharge: study of the treatment process, dynamic wettability and interactions with a waterborne coating}, \emph{{Holzforschung}}, 2021.
	
	\item {\textbf{Pierre Kibleur}, Shravan R.Tata, Nathan Greiner, Sara Conti, Beatrice Barra, Katie Zhuang, Melanie Kaeser, Auke Ijspeert, and Marco Capogrosso}. {Spatiotemporal maps of proprioceptive inputs to the cervical spinal cord during three-dimensional reaching and grasping}, \emph{IEEE Transactions on Neural Systems and Rehabilitation Engineering}, 2020.
	
	\item {Yuriy Sinchuk, \textbf{Pierre Kibleur}, Jan Aelterman, Matthieu N. Boone, and Wim Van Paepegem}. {Variational and deep learning segmentation of very-low-contrast X-ray computed tomography images of carbon/epoxy woven composites}, \emph{Materials}, 2020.   
	
	\item {Wanzhao Li, Zheng Zhang, Guoqiang Zhou, \textbf{Pierre Kibleur}, Changtong Mei, Jiangtao Shi, Joris Van Acker, and Jan Van den Bulcke}. {The effect of structural changes on the compressive strength of LVL}, \emph{Wood Science and Technology}, 2020.     

	\item  {Wanzhao Li, Chaoyi Chen, Jiangtao Shi, Changtong Mei, \textbf{Pierre Kibleur}, Joris Van Acker, and Jan Van den Bulcke}. {Understanding the mechanical performance of OSB in compression tests}, \emph{Construction and Building Materials}, 2020.
	
	\item {Gerrit Ralf Surup, Henrik Kofoed Nielsen, Marius Gro{\ss}arth, R{\"{u}}diger Deike, Jan Van den Bulcke, \textbf{Pierre Kibleur}, Michael M{\"{u}}ller, Mirko Ziegner, Elena Yazhenskikh, Sergey Beloshapkin, James J. Leahy, and Anna Trubetskaya}. {Effect of operating conditions and feedstock composition on the properties of manganese oxide or quartz charcoal pellets for the use in ferroalloy industries}, \emph{Energy}, 2020.
	
	\item {Faezeh Rahbar, Ali Marjovi, \textbf{Pierre Kibleur}, and Alfio Martinoli, A 3-D bio-inspired odor source localization and its validation in realistic environmental conditions, \emph{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, 2017.}
\end{itemize}
       
    \section{Conference contributions}
    \begin{itemize}
    	\item  {\textbf{Pierre Kibleur}, Zaira Manigrasso, Wannes Goethals, Jan Aelterman, Matthieu N. Boone, Joris Van Acker, and Jan Van den Bulcke}. {Microscopic deformations in MDF swelling: a unique 4D-CT characterization}, 5\textsuperscript{th} International Conference on Tomography of Materials \& Structures, 2022 (received the ICTMS student poster award). 
    	
    	\item {\textbf{Pierre Kibleur}, Zaira Manigrasso, Wannes Goethals, Jan Aelterman, Matthieu N. Boone, Joris Van Acker, and Jan Van den Bulcke}. Caract\'erisation temporelle des d\'eformations microscopiques dans les panneaux de fibres en conditions humides. 10\textsuperscript{\`emes} journ\'ees du GDR 3544 ``Sciences du bois'', 2021.
    	
    	\item \textbf{Pierre Kibleur}, Wanzhao Li, Jan Van den Bulcke, and Joris Van Acker. 4D X-ray CT studies on wood-based panels at UGCT-Woodlab. 63rd International Convention of Society of Wood Science and Technology, 2020.
    	
    	\item \textbf{Pierre Kibleur}. Advanced X-ray CT scanning for lignocellulosic materials. 4\textsuperscript{th} International EPNOE Junior Scientist Meeting, 2020 (invited speaker).
    	
    	\item  \textbf{Pierre Kibleur}, Romain Lehnebach, Jan Van den Bulcke, and Joris Van Acker. Determining the local deformation fields of wood-based panels set in moist conditions. 8\textsuperscript{\`emes} journ\'ees du GDR 3544 ``Sciences du bois'', 2019.
    	
    	\item  \textbf{Pierre Kibleur}, Jan Van den Bulcke, and Joris Van Acker. Hygroscopic deformation of wood-based panels: a 4D $\mu$CT study. Measuring by Light meets OPTIMESS, 2019.
    \end{itemize}    
    \section{Other}
		\OneLiner[Research stays and trainings abroad]{\begin{itemize}
				\item Universit\'e de Pau et des Pays de l'Adour: X-ray imaging
				\item Technical University of Denmark: X-ray imaging
				\item Delft University of Technology: robotics
				\item Motek Medical (Amsterdam): robotics
			\end{itemize}}{\begin{itemize}
			\item[] \hfill 2019
			\item[] \hfill 2019
			\item[] \hfill 2017
			\item[] \hfill 2017
			\end{itemize}}
		\OneLiner[Reviewer for]{\begin{itemize}
				\item Holzforschung
				\item Studies in Conservation
			\end{itemize}}{}
\end{document}


    \begin{itemize}    	    	
	\item \textbf{Pierre Kibleur}, Benjamin Blykers, Matthieu N. Boone, Luc Van Hoorebeke, Joris Van Acker, and Jan Van den Bulcke. Detecting thin adhesive coatings in wood fiber materials with laboratory-based Dual-Energy Computed Tomography (DECT), \emph{Scientific Reports}, 2022.
	
	\item  {\textbf{Pierre Kibleur}, Zaira Manigrasso, Wannes Goethals, Jan Aelterman, Matthieu N. Boone, Joris Van Acker, and Jan Van den Bulcke}. {Microscopic deformations in MDF swelling: a unique 4D-CT characterization}, \emph{Materials and Structures}, 2022.
	
	\item  {\textbf{Pierre Kibleur}, Jan Aelterman, Matthieu N. Boone, Jan Van den Bulcke, and Joris Van Acker}. {Deep learning segmentation of wood fiber bundles in fiberboards}, \emph{Composites Science and Technology},  2022.
	
	\item Haichao Li, Jan Van den Bulcke, \textbf{Pierre Kibleur}, Orly Mendoza, Stefaan De Neve, and Steven Sleutel. Soil textural control on moisture distribution at the microscale and effect on organic matter mineralization, \emph{Soil Biology and Chemistry}, 2022.
	
	\item {Wanzhao Li, Zheng Zhang, Changtong Mei, \textbf{Pierre Kibleur}, Joris Van Acker, and Jan Van den Bulcke}. {Understanding the mechanical strength and dynamic structural changes of wood-based products using X-ray computed tomography}, \emph{Wood Material Science {\&} Engineering}, 2022.
	
	\item {Yuriy Sinchuk, \textbf{Pierre Kibleur}, Jan Aelterman, Matthieu N. Boone, and Wim Van Paepegem}. {Geometrical and deep learning approaches for instance segmentation of CFRP fiber bundles in textile composites}, \emph{Composite Structures}, 2021.
	
	\item {Jure \v{Z}}igon, Matja{\v{z}} Pavli{\v{c}}, \textbf{Pierre Kibleur}, Jan Van den Bulcke, Marko Petri{\v{c}}, Joris Van Acker, and Sebastian Dahle. {Treatment of wood with atmospheric plasma discharge: study of the treatment process, dynamic wettability and interactions with a waterborne coating}, \emph{{Holzforschung}}, 2021.
	
	\item {\textbf{Pierre Kibleur}, Shravan R.Tata, Nathan Greiner, Sara Conti, Beatrice Barra, Katie Zhuang, Melanie Kaeser, Auke Ijspeert, and Marco Capogrosso}. {Spatiotemporal maps of proprioceptive inputs to the cervical spinal cord during three-dimensional reaching and grasping}, \emph{IEEE Transactions on Neural Systems and Rehabilitation Engineering}, 2020.
	
	\item {Yuriy Sinchuk, \textbf{Pierre Kibleur}, Jan Aelterman, Matthieu N. Boone, and Wim Van Paepegem}. {Variational and deep learning segmentation of very-low-contrast X-ray computed tomography images of carbon/epoxy woven composites}, \emph{Materials}, 2020.   
	
	\item {Wanzhao Li, Zheng Zhang, Guoqiang Zhou, \textbf{Pierre Kibleur}, Changtong Mei, Jiangtao Shi, Joris Van Acker, and Jan Van den Bulcke}. {The effect of structural changes on the compressive strength of LVL}, \emph{Wood Science and Technology}, 2020. 
	
	\item  {Wanzhao Li, Chaoyi Chen, Jiangtao Shi, Changtong Mei, \textbf{Pierre Kibleur}, Joris Van Acker, and Jan Van den Bulcke}. {Understanding the mechanical performance of OSB in compression tests}, \emph{Construction and Building Materials}, 2020.
	
	\item {Gerrit Ralf Surup, Henrik Kofoed Nielsen, Marius Gro{\ss}arth, R{\"{u}}diger Deike, Jan Van den Bulcke, \textbf{Pierre Kibleur}, Michael M{\"{u}}ller, Mirko Ziegner, Elena Yazhenskikh, Sergey Beloshapkin, James J. Leahy, and Anna Trubetskaya}. {Effect of operating conditions and feedstock composition on the properties of manganese oxide or quartz charcoal pellets for the use in ferroalloy industries}, \emph{Energy}, 2020.
	
	\item {Faezeh Rahbar, Ali Marjovi, \textbf{Pierre Kibleur}, and Alfio Martinoli, A 3-D bio-inspired odor source localization and its validation in realistic environmental conditions, \emph{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, 2017.}
\end{itemize}






    \section{\TwoColumns[Languages]{Free time}}
\OneLiner[English]{Fluent}{Competition rowing }
\OneLiner[French]{Native speaker \hfill}{(2021 Belgian champ.)}
\OneLiner[Russian]{Limited proficiency\hfill}{Running, swimming}
\OneLiner[Dutch]{Notions\hfill}{Flute, tenor saxophone}
