\documentclass[oneside, english, 10pt, a4paper]{memoir}
\usepackage{CV_template}
\usepackage{enumitem}

\begin{document}
	
	\section{Peer-reviewed publications}
	\begin{itemize}[leftmargin=*]   	    	
		\item Jan Van den Bulcke, Louis Verschuren, Ruben De Blaere, Simon Vansuyt, Maxime Dekegeleer, \textbf{Pierre Kibleur}, Olivier Pieters, Tom De Mil, Wannes Hubau, Hans Beeckman, Joris Van Acker, Francis wyffels. An automated high-throughput pipeline for high-resolution analysis of wood anatomy on stem disk and increment core surfaces, \emph{Plant Methods}, in review.
		
		\item Noemi De Roo, \textbf{Pierre Kibleur}, Liesbeth Temmerman, Ronald Verbeeck, Matthieu Boone, Guy De Pauw. The effect of cryopreservation on enamel microcracks – a µCT analysis using a deep learning algorithm, \emph{Cryobiology}, in review. 
		
		\item Szabolcs Korsós, \textbf{Pierre Kibleur}, Ivan Josipovic, Matthieu Boone, Lieven Vlaminck. Manual versus reciprocating endodontic debridement of equine cheek teeth: micro-computed tomography findings, \emph{Equine Veterinary Journal}, in review.
		
		\item Margherita Martini, Pierre Francus, Laurenz Schröer, Florian Buyse, \textbf{Pierre Kibleur}, Veerle Cnudde, Leonardo Di Schiavi Trotta, Philippe Després. Characterization of geological samples with dual-energy XCT: a comparison of three different scanners, \emph{Geostandards and Geoanalytical Research}, in review.
		
		\item Sophie Debaenst, Tamara Jarayseh, Hanna De Saffel, Jan Willem Bek, Matthieu Boone, Ivan Josipovic, \textbf{Pierre Kibleur}, Ronald Y. Kwon, Paul Coucke, and Andy Willaert. Crispant analysis in zebrafish as a tool for rapid functional screening of disease-causing genes for bone fragility, \emph{eLife}, 2024.
		
		\item Caori Organista, Ruizhi Tang, Zhitian Shi, Konstantins Jefimovs, Daniel Josell, Lucia Romano, Simon Spindler, \textbf{Pierre Kibleur}, Benjamin Blykers, Marco Stampanoni, and Matthieu N. Boone. Implementation of a dual-phase grating interferometer for multi-scale characterization of building materials by tunable dark-field imaging, \emph{Scientific Reports}, 2024.
		
		\item Sofie Dierickx, Siska Genbrugge, Hans Beeckman, Wannes Hubau, \textbf{Pierre Kibleur}, and Jan Van den Bulcke. Non-destructive wood identification using X-ray µCT scanning: which resolution do we need?, \emph{Plant Methods}, 2024.
		
		\item Zaira Manigrasso, Wannes Goethals, \textbf{Pierre Kibleur}, Matthieu N. Boone, Wilfried Philips, and Jan Aelterman. Image-Based Crack Detection Using Total Variation Strain DVC Regularization, \emph{Applied Sciences}, 2023.
		
		\item \textbf{Pierre Kibleur}, Benjamin Blykers, Matthieu N. Boone, Luc Van Hoorebeke, Joris Van Acker, and Jan Van den Bulcke. Detecting thin adhesive coatings in wood fiber materials with laboratory-based Dual-Energy Computed Tomography (DECT), \emph{Scientific Reports}, 2022.
		
		\item  {\textbf{Pierre Kibleur}, Zaira Manigrasso, Wannes Goethals, Jan Aelterman, Matthieu N. Boone, Joris Van Acker, and Jan Van den Bulcke}. {Microscopic deformations in MDF swelling: a unique 4D-CT characterization}, \emph{Materials and Structures}, 2022.
		
		\item  {\textbf{Pierre Kibleur}, Jan Aelterman, Matthieu N. Boone, Jan Van den Bulcke, and Joris Van Acker}. {Deep learning segmentation of wood fiber bundles in fiberboards}, \emph{Composites Science and Technology},  2022.
		
		\item Haichao Li, Jan Van den Bulcke, \textbf{Pierre Kibleur}, Orly Mendoza, Stefaan De Neve, and Steven Sleutel. Soil textural control on moisture distribution at the microscale and effect on organic matter mineralization, \emph{Soil Biology and Chemistry}, 2022.
		
		\item {Wanzhao Li, Zheng Zhang, Changtong Mei, \textbf{Pierre Kibleur}, Joris Van Acker, and Jan Van den Bulcke}. {Understanding the mechanical strength and dynamic structural changes of wood-based products using X-ray computed tomography}, \emph{Wood Material Science {\&} Engineering}, 2022.
		
		\item {Yuriy Sinchuk, \textbf{Pierre Kibleur}, Jan Aelterman, Matthieu N. Boone, and Wim Van Paepegem}. {Geometrical and deep learning approaches for instance segmentation of CFRP fiber bundles in textile composites}, \emph{Composite Structures}, 2021.
		
		\item {Jure \v{Z}}igon, Matja{\v{z}} Pavli{\v{c}}, \textbf{Pierre Kibleur}, Jan Van den Bulcke, Marko Petri{\v{c}}, Joris Van Acker, and Sebastian Dahle. {Treatment of wood with atmospheric plasma discharge: study of the treatment process, dynamic wettability and interactions with a waterborne coating}, \emph{{Holzforschung}}, 2021.
		
		\item {\textbf{Pierre Kibleur}, Shravan R.Tata, Nathan Greiner, Sara Conti, Beatrice Barra, Katie Zhuang, Melanie Kaeser, Auke Ijspeert, and Marco Capogrosso}. {Spatiotemporal maps of proprioceptive inputs to the cervical spinal cord during three-dimensional reaching and grasping}, \emph{IEEE Transactions on Neural Systems and Rehabilitation Engineering}, 2020.
		
		\item {Yuriy Sinchuk, \textbf{Pierre Kibleur}, Jan Aelterman, Matthieu N. Boone, and Wim Van Paepegem}. {Variational and deep learning segmentation of very-low-contrast X-ray computed tomography images of carbon/epoxy woven composites}, \emph{Materials}, 2020.   
		
		\item {Wanzhao Li, Zheng Zhang, Guoqiang Zhou, \textbf{Pierre Kibleur}, Changtong Mei, Jiangtao Shi, Joris Van Acker, and Jan Van den Bulcke}. {The effect of structural changes on the compressive strength of LVL}, \emph{Wood Science and Technology}, 2020.     
		
		\item  {Wanzhao Li, Chaoyi Chen, Jiangtao Shi, Changtong Mei, \textbf{Pierre Kibleur}, Joris Van Acker, and Jan Van den Bulcke}. {Understanding the mechanical performance of OSB in compression tests}, \emph{Construction and Building Materials}, 2020.
		
		\item {Gerrit Ralf Surup, Henrik Kofoed Nielsen, Marius Gro{\ss}arth, R{\"{u}}diger Deike, Jan Van den Bulcke, \textbf{Pierre Kibleur}, Michael M{\"{u}}ller, Mirko Ziegner, Elena Yazhenskikh, Sergey Beloshapkin, James J. Leahy, and Anna Trubetskaya}. {Effect of operating conditions and feedstock composition on the properties of manganese oxide or quartz charcoal pellets for the use in ferroalloy industries}, \emph{Energy}, 2020.
		
		\item {Faezeh Rahbar, Ali Marjovi, \textbf{Pierre Kibleur}, and Alfio Martinoli, A 3-D bio-inspired odor source localization and its validation in realistic environmental conditions, \emph{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, 2017.}
	\end{itemize}
\end{document}
